--
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CWP.dataset

<!-- badges: start -->
[![R-CMD-check](https://github.com/bastienird/CWP.dataset/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bastienird/CWP.dataset/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/bastienird/CWP.dataset/graph/badge.svg)](https://app.codecov.io/gh/bastienird/CWP.dataset)
<!-- badges: end -->

CWP.dataset is an R package designed for analyzing and comparing fisheries datasets which are compliant with the CWP standards.

It includes functions for:
✔ Data harmonization and structuring
✔ Spatiotemporal analyses
✔ Conversion between different measurement units (e.g., tons ↔ numbers)
✔ Comparing nominal and georeferenced datasets

## Installation

You can install the development version of CWP.dataset from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("bastienird/CWP.dataset")
```

## Documentation

Full documentation website on: https://bastienird.github.io/CWP.dataset

## Example


```{r}
fusen::draw_package_structure()
```

