```{r setuprmd, include = FALSE, echo=FALSE}

knitr::opts_chunk$set(warning = FALSE)
res <- knitr::knit_child(system.file("rmd/Setup_markdown.Rmd", package = "CWP.dataset"), quiet = TRUE, envir = environment())

```

# Summary of the final provided data : `r ifelse(exists("datasetname"), datasetname, gsub("_", "", entity$identifiers[["id"]]))`

```{r pathtoqsfinal}

if(exists("path_to_qs_final")){
  
  child_env_last_result <- qs::qread(path_to_qs_final)
  child_env_last <- list2env(as.list(child_env_last_result), parent = new.env())
  
} else {
  
  child_env_last <- list2env(as.list(child_env_last_result), parent = new.env())
  
}
```


```{r analysislast, message=TRUE, warning=TRUE, include=FALSE}

rm(child_env_last_result)
gc()
res_last <- knitr::knit_child(system.file("rmd/comparison.Rmd", package = "CWP.dataset"), quiet = TRUE, envir = child_env_last)

# rm(child_env_last_result, envir = environment())
rm(child_env_last, envir = environment())
gc()

```

```{r catanalyslast, echo=FALSE, results='asis'}

cat(res_last, sep =  "\\clearpage")

```


```{r cleaninganalysislast, include=FALSE}

rm(res_last, envir = environment())
gc()

```

\clearpage

# Summary of the treatment done on the data (comparison between the Initial data and the data resulting from treatments)

```{r pathtoqssummary}

if(exists("path_to_qs_summary")){
  
  child_env_first_to_last_result <- qs::qread(path_to_qs_summary)
  child_env_first_to_last <- list2env(as.list(child_env_first_to_last_result), parent = new.env())
  
} else {
  
  child_env_first_to_last <- list2env(as.list(child_env_first_to_last_result), parent = new.env())
  
}

```

```{r complastfirst, include=FALSE, results='asis'}


res_comparison_first_to_last <- knitr::knit_child(system.file("rmd/comparison.Rmd", package = "CWP.dataset"), quiet = TRUE, envir = child_env_first_to_last)

rm(child_env_first_to_last)
# rm(child_env_first_to_last_result)
gc()

```


```{r complastfirstcat, echo=FALSE, results='asis'}

cat(res_comparison_first_to_last, sep =  "\\clearpage")

```


```{r include=FALSE}

rm(res_comparison_first_to_last)
gc()

```

\clearpage


# Analyse of the processing of the data

The following table recap all the treatment done on the mapped and standardized rawdata provided by tRFMOs.

```{r results='asis'}

qflextable2(process_fisheries_data_list$reduced, captionn =process_fisheries_data_list$fig.capp, columns_to_color = process_fisheries_data_list$columns_to_color,  pgwidth = 6, save_folder = "Summary", fig.pathinside = fig.path)

```

```{r message=FALSE, warning=FALSE}

save_image(title= process_fisheries_data_list$fig.capp, plott = process_fisheries_data_list$cowplot, folder = "Summary", fig.pathinside = fig.path)

```


```{r evolamountduringprocess,  echo=FALSE, results='asis', fig.cap = process_fisheries_data_list$fig.capp, out.width='100%'}

process_fisheries_data_list$cowplot

```
