---
title: "Main_caracteristics_of_dataset"
output: html_document
---

`r if(main_title){CWP.dataset::cat_title("# Main characteristics of the two datasets", child_headerinside = child_header)}`

```{r timecoverage, echo=FALSE, results='asis', eval = (exists("time_coverage_analysis_list", envir =environment()) && !is.null(time_coverage_analysis_list)), include=FALSE}

time_dimension_list_groupped_diff_image_knit <- mapply(FUN = CWP.dataset::knitting_plots_subfigures, plot = time_coverage_analysis_list$plots, title = time_coverage_analysis_list$titles, MoreArgs = list(folder = "Temporal", fig.pathinside = fig.path))

```

`r if(exists("time_coverage_analysis_list", envir =environment()) && !is.null(time_coverage_analysis_list)){CWP.dataset::cat_title("## Time coverage", child_headerinside = child_header)}`

```{r temporalcoveragelistplotknitting, echo=FALSE, results='asis', eval = (exists("time_coverage_analysis_list", envir =environment()) && !is.null(time_coverage_analysis_list))}

cat(unlist(time_dimension_list_groupped_diff_image_knit, recursive = FALSE), sep = "
")

```

\clearpage

```{r results='asis', eval = (exists("spatial_coverage_analysis_list", envir =environment()) && !is.null(spatial_coverage_analysis_list))}

map_unit_knit_list <- mapply(FUN = CWP.dataset::knitting_plots_subfigures, plot = spatial_coverage_analysis_list$plots, title = spatial_coverage_analysis_list$titles)

```

`r if(exists("spatial_coverage_analysis_list", envir =environment()) && !is.null(spatial_coverage_analysis_list)){CWP.dataset::cat_title("## Spatial coverage", child_headerinside = child_header)}`

```{r spatialcoverage, eval=(exists("spatial_coverage_analysis_list", envir =environment()) && !is.null(spatial_coverage_analysis_list)), echo=FALSE, message=FALSE, results='asis'}

cat(spatial_coverage_analysis_list$child_text)

cat(unlist(map_unit_knit_list), sep = "
")

```

\clearpage

`r if(exists("other_dimension_analysis_list", envir =environment()) && !is.null(other_dimension_analysis_list)){CWP.dataset::cat_title("## Coverage for other dimensions", child_headerinside = child_header)}`

We check the distribution of the value of each dimension and each unit.

```{r pie-charts-multiple, eval=(exists("other_dimension_analysis_list", envir =environment()) && !is.null(other_dimension_analysis_list) &&!unique_analyse), message=FALSE, warning=FALSE, include=FALSE}

pie_chart_knit <- mapply(FUN = CWP.dataset::knitting_plots_subfigures, plot = other_dimension_analysis_list$figures, title = other_dimension_analysis_list$dimension_title_subfigures, MoreArgs = list(folder = "Piechartdimensions", fig.pathinside = fig.path))
# bar_chart_knit <- mapply(FUN = CWP.dataset::knitting_plots_subfigures, plot = other_dimension_analysis_list$barplots, title = other_dimension_analysis_list$dimension_title_subfigures, MoreArgs = list(folder = "Barplot", fig.pathinside = fig.path))

```

```{r otherdimensionanalysis, eval=(exists("other_dimension_analysis_list", envir =environment()) && !is.null(other_dimension_analysis_list) && !unique_analyse), echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

cat(unlist(pie_chart_knit), sep = "
")

```

```{r subfigures, eval=(exists("other_dimension_analysis_list", envir =environment()) && !is.null(other_dimension_analysis_list) && unique_analyse), message=FALSE, warning=FALSE, results='asis'}

CWP.dataset::render_subfigures(plots_list = other_dimension_analysis_list$figures , titles_list = other_dimension_analysis_list$dimension_title_subfigures, general_title = "Other dimensions")

```

```{r subfigures, eval=FALSE, message=FALSE, warning=FALSE, results='asis'}

CWP.dataset::render_subfigures(plots_list = barplots, titles_list = dimension_title_subfigures, general_title = "Other dimensions")

```

```{r otherdimensionanalysisbarplots, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

cat(unlist(bar_chart_knit), sep = "
")

```

\clearpage
